\documentclass[letterpaper,11pt]{article}

\usepackage{hyperref}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.45in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
% \usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-6pt}}

\newcommand{\award}[2]{
    \begin{tabular*}{6.78in}{l@{\extracolsep{\fill}}r}
        \text{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Yu Hou}  & \\
    https://github.com/hyhugh &  hy1995@gmail.com \\
    https://www.linkedin.com/in/yu-hou-8133b9108/ & yu.hou@unsw.edu.au
\end{tabular*}
\vspace{-10pt}

\resheading{Education}
\begin{itemize}
    \item
        \ressubheading{University of New South Wales}{Kensington, NSW}{Bachelor of Computer Science}{March. 2017 - Sep. 2019}
        \begin{itemize}
                \resitem{Graduated with High Distinction WAM 88 (GPA 3.95/4)}
                \resitem{Relevant courses: Advanced Operating Systems, Distributed Systems, Programming Languages and Compilers}
        \end{itemize}
    \item
        \ressubheading{University of New South Wales}{Kensington, NSW}{Bachelor of Computer Science (Honours)}{Oct. 2019 - present}
        \begin{itemize}
                \resitem{Thesis topic: Power management on seL4}
        \end{itemize}
\end{itemize}
\vspace{-10pt}

\resheading{Work Experience}
\begin{itemize}
    \item
        \ressubheading{CSIRO's Data61}{}{Casual Operating Systems Engineer}{Feb. 2019 - present}
        \begin{itemize}
                \resitem{ Implemented a devicetree generator, which can be used to generate a sub-devicetree for partitioning devices for different guest VMs }
                \resitem{ Worked on nested seL4 systems project, implemented IRQ control capability virtualization and resource management }
                \resitem{ Worked on various build system(cmake) improvement projects }
        \end{itemize}
\end{itemize}
\vspace{-10pt}

\resheading{Notable Work}
\begin{itemize}
    \item
        \ressubheading{Simple Operating System}{}{Advanced Operating Systems, COMP9242}{June. 2019 - Sep. 2019}
        \begin{itemize}
                \resitem{ Implemented a monolithic kernel on top of the seL4 microkernel }
                \resitem{ Achieved the highest I/O throughput in class with carefully designed filesystem cache }
        \end{itemize}

    \item
        \ressubheading{VC Compiler}{}{Programming Languages and Compilers, COMP3131}{Feb. 2019 - May. 2019}
        \begin{itemize}
                \resitem{ Implemented a simple C variant compiler frontend }
                \resitem{ Implemented scanner, parser, type checker and code generator }
                \resitem{ The code generator can generate Jasmin assembly code running on JVM }
        \end{itemize}
\end{itemize}

\vspace{-10pt}

\resheading{Awards}
\begin{description}
    \item
        \award{COMP9242 Prize (for the best performance in COMP9242 Advanced Operating Systems)}{2019}
    \item
        \award{Faculty of Engineering Dean's Honours List}{2018}
    \item
        \award{UNSW Taste of Research Summer Scholarship}{2018}
\end{description}

\vspace{-10pt}

\resheading{Skills}

\begin{itemize}
    \item
        Proficient in C, Java, Python and Haskell, Familiar with C++
    \item
        Familiar with performance optimization and program profiling
    \item
        Strong low level programming/debugging skill

\end{itemize}
\end{document}
